---
title: "Classification with Measurement Error"
author: "Sarah Shy, Jonathan Hehir"
date: "April 21, 2020"
bibliography: sources.bib
csl: american-statistical-association.csl
output: beamer_presentation

# For fancy beamer theme, we can use this instead of the `output` line above.
# But it requires having the theme installed,
# and I fear we could have cross-platform issues with LaTeX rendering.
# Skipping for now, but we can play with it.
#
# output:
#  beamer_presentation:
#    theme: metropolis
#    latex_engine: xelatex
---

```{r include=FALSE}
library(tidyverse)
library(mvtnorm)
set.seed(557421)
```

(this slide is blank)

# Introduction

## What is measurement error?

**Measurement error** is the difference between a measured quantity and its true value.

. . .

In many statistical scenarios, we assume that our variables are perfect measurements from some sample.

. . .

This is often **false**. In many cases, we know our measurements are inaccurate.

. . .

In especially nice cases, we know **how inaccurate** they are.

## Applications of Measurement Error

Situations where we know our measurement error include:

- Astronomy data (we'll come back to this)
- Privacy applications
  - Intentionally adding noise to observations is a common method for achieving privacy. We choose the amount of noise to add.
- Earthquake data?
  - Would need to ask our friend Ian Lee about this.
- Many instruments used for measurement.

## Example: A Clean Sample

Easily separable classes. No measurement error.

- 500 observation
- 2 classes:
$X_1, \dots, X_250 \sim N(\mu_1, \Sigma_1)$
$X_251, \dots, X_500 \sim N(\mu_2, \Sigma_2)$
$\epsilon \sim N(\mathbf0, 1 0 0 3$

x | y | errX | errY
---- | ---- | ---- | ----
34.4 | 12 | 1 | 2
34.4 | 12 | 1 | 2


```{r echo=F, warning=F}
toy <- new.env()
source("../Toys/svm_measurement_error_toy.R", toy)
attach(toy)

data <- make_base_data()
plot_data(data)
```

---

## Example: Noisy Sample

This is the exact same sample, but with some error added to each point.

```{r echo=F}
noisy <- noisify_data(data)
plot_data_with_error(noisy)
```

## Example classifier performance

Fitting a basic linear SVM to the above yields the following accuracies:

```{r include=F}
d_acc <- 100*svm_metrics(data)$accuracy
n_acc <- 100*svm_metrics(noisy)$accuracy
```

Original Sample | Noisy Sample
----------------|----------------
`r sprintf("%0.1f", d_acc)`% | `r sprintf("%0.1f", n_acc)`%

. . .

**Can we trust this accuracy estimate?**

## Simulating Measurement Error

Using that same original sample, we repeat this process 500 times to obtain the following distribution of classifier accuracy:

```{r cache=T, echo=F}
# simulate measurement error on one clean observation
sim_results_me <- run_simulations(data, 500, 1)

#ggplot(sim_results_me) + geom_boxplot(aes(y = accuracy)) +
#  scale_y_continuous(labels = scales::percent) +
#  ylab("Accuracy")

ggplot(sim_results_me) + geom_histogram(aes(x = accuracy), binwidth = 0.01, alpha = 0.5, color = "#000000") +
  xlab("Accuracy") +
  ylab("Frequency")

detach(toy)
```

---

\LARGE Can we estimate that distribution without access to the clean sample?

# Ideas

## What do we want?

- Want a method for estimating uncertainty in classification performance that can be used for any classifier.
In our project:
- We use Gaussian perturbation based on known measurement error
- As a bonus:
  - quantify class stability
  - probabilities for each observation (think, soft classifier via ensemble learning)

## How do we do it?

Insert pipeline here. Sarah's job. Parallel is good.

# Real Data

## Astronomy

Here's some data from astronomers [@example2014].

. . .

There are literally rocket scientists.

. . .

Just kidding. They don't have rockets.

. . .

But I bet they wish they did.

## Results

In our testing, our method performs amazingly. It is so good.
Show confidence intervals
Show probabiities? i.e. if all perturbed sets predict obs 1 to be class 1, prob = 1

<!--
var(sim_results$accuracy)
var(sim_results_noisy$accuracy)


-->

## Future directions + related work
- Gaussian perturbation in clustering setting (mostly used for cluster stability)
  - Note (remove text) In literature, usually choose a fixed variance. Here, use known measurement error so that our measure of cluster stability is essentially a function of the known measurement error
- tbd

# The End

## Bibliography

\fontsize{7}{7}\selectfont
