---
title: "Classification with Measurement Error"
author: "Sarah Shy, Jonathan Hehir"
date: "April 21, 2020"
bibliography: sources.bib
csl: american-statistical-association.csl
output: beamer_presentation

# For fancy beamer theme, we can use this instead of the `output` line above.
# But it requires having the theme installed,
# and I fear we could have cross-platform issues with LaTeX rendering.
# Skipping for now, but we can play with it.
#
# output:
#  beamer_presentation:
#    theme: metropolis
#    latex_engine: xelatex
---

```{r include=FALSE}
library(tidyverse)
library(mvtnorm)
set.seed(557)
```

(this slide is blank)

# Introduction

## What is measurement error?

In many statistical scenarios, we assume that our variables are exact measurements from some sample.

. . .

This is often **false**.

(An example citation: @example2014.)

## Example: A Clean Sample

This is an example of a nice sample.

```{r echo=F, warning=F}
toy <- new.env()
attach(toy)
source("../Toys/svm_measurement_error_toy.R")

data <- make_base_data()
plot_data(data)
```

---

## Example: Noisy Sample

This is the exact same sample, but with some error added to each point.

```{r echo=F}
noisy <- noisify_data(data)
plot_data_with_error(noisy)
```

## What happens now?

blah blah


<!--
data <- make_base_data()
plot_data(data)

noisy <- noisify_data(data)
plot_data(noisy)

svm_metrics(data)
svm_metrics(noisy)

# simulate actual measurement error
sim_results <- run_simulations(data, 500)

# simulate measurement error on top of a given noisy observation
sim_results_noisy <- run_simulations(noisy, 500)

# simulate measurement error with double noise
sim_results_double <- run_simulations(data, 500, 2)

sim_results_combined <- bind_rows(
  sim_results %>% add_column(noise = "on true data"),
  sim_results_double %>% add_column(noise = "on true data twice"),
  sim_results_noisy %>% add_column(noise = "on noisy observation")
)

ggplot(sim_results_combined) + geom_boxplot(aes(x = noise, y = accuracy))
var(sim_results$accuracy)
var(sim_results_noisy$accuracy)


-->

# The End

## Bibliography

