---
title: "Classification with Measurement Error"
author: "Sarah Shy, Jonathan Hehir"
date: "April 21, 2020"
bibliography: sources.bib
csl: american-statistical-association.csl
output: beamer_presentation

# For fancy beamer theme, we can use this instead of the `output` line above.
# But it requires having the theme installed,
# and I fear we could have cross-platform issues with LaTeX rendering.
# Skipping for now, but we can play with it.
#
# output:
#  beamer_presentation:
#    theme: metropolis
#    latex_engine: xelatex
---

```{r include=FALSE}
library(tidyverse)
library(mvtnorm)
set.seed(557421)
```

(this slide is blank)

# Introduction

## What is measurement error?

**Measurement error** is the difference between a measured quantity and its true value.

. . .

In many statistical scenarios, we assume that our variables are perfect measurements from some sample.

. . .

This is often **false**. In many cases, we know our measurements are inaccurate.

. . .

In especially nice cases, we know **how inaccurate** they are.

## Applications of Measurement Error

Situations where we know our measurement error include:

- Astronomy data
  - DETAILS NEEDED HERE
- Privacy applications
  - Intentionally adding noise to observations is a common method for achieving privacy. Here we know the exact distribution of the real data.
- Earthquake data?
  - Would need to ask our friend Ian Lee about this.

## Toy Example: A Clean Sample

This is an example of a particularly nice sample.

```{r echo=F, warning=F}
toy <- new.env()
source("../Toys/svm_measurement_error_toy.R", toy)
attach(toy)

data <- make_base_data()
plot_data(data)
```

## Toy Example: A Clean Sample

Let's perturb this data using the following measurement error distribution:

```{r echo=F, warning=F}
plot_data_with_error(data)
```

---

## Toy Example: Noisy Sample

Now we have this mess:

```{r echo=F}
noisy <- noisify_data(data)
plot_data(noisy)
```

## Toy Example: Classifier Performance

Fitting a basic linear SVM to the above yields the following accuracies:

```{r include=F}
d_acc <- 100*svm_metrics(data)$accuracy
n_acc <- 100*svm_metrics(noisy)$accuracy
```

Clean Sample | Noisy Sample
-------------|----------------
`r sprintf("%0.1f", d_acc)`% | `r sprintf("%0.1f", n_acc)`%

. . .

**Can we trust this accuracy estimate?**

## Toy Example: Simulating Measurement Error

Using that same original sample, we repeat this process 500 times to obtain the following distribution of classifier accuracy:

```{r cache=T, echo=F}
# simulate measurement error on one clean observation
sim_results_me <- run_simulations(data, 500, 1)

#ggplot(sim_results_me) + geom_boxplot(aes(y = accuracy)) +
#  scale_y_continuous(labels = scales::percent) +
#  ylab("Accuracy")

ggplot(sim_results_me) + geom_histogram(aes(x = accuracy), binwidth = 0.01, color = "#000000", fill= "#ffaa33") +
  xlab("Accuracy") +
  ylab("Frequency")

detach(toy)
```

---

\LARGE Can we estimate that distribution if we only observe the noisy sample?

---

<!-- add box plots here -->

<!-- add plot of 500 SVM boundaries -->

<!-- add plot of P(class 1) estimated from ensemble of 500 SVMs, ROFL -->


# Ideas

## What do we want?

- Want a method for estimating uncertainty in classification performance that can be used for any classifier.
- etc.

## How do we do it?

Insert pipeline here.

# Real Data

## Astronomy

Here's some data from astronomers [@example2014].

. . .

There are literally rocket scientists.

. . .

Just kidding. They don't have rockets.

. . .

But I bet they wish they did.

## Results

In our testing, our method performs amazingly. It is so good.

<!--
var(sim_results$accuracy)
var(sim_results_noisy$accuracy)


-->

# The End

## Bibliography

\fontsize{7}{7}\selectfont
